### 2010-09-28 Documentation/part1.tex
Further functions added to manual

In some cases, it is necessary to obtain information from the loaded \AEDL\
files. This and the next sections are marked as advanced because knowledge of \AEDL\ is
required, \ie,  the reader should be familiar with Part~\ref{part:2} of the manual.
%
Very basic information is supplied with
\begin{function}
\GLBNS{GetEminEmax}
{\tt int glbGetEminEmax(int experiment, double *emin, double *emax)} returns the
energy range [{\tt emin}, {\tt emax}] covered by the binning as defined in the \AEDL\ file for the experiment
{\tt experiment}.
\end{function}
\begin{function}
\GLBNS{GetEnergyWindow} \label{glbGetEnergyWindow}
{\tt int glbGetEnergyWindow(int exp, int rule, double *low, double *high)} returns the
energy window [{\tt low}, {\tt high}] defined in the \AEDL\ file for the experiment
{\tt exp} and rule {\tt rule}. See also {\tt glbSetEnergyWindow} on page~\pageref{glbSetEnergyWindow}.
\end{function}
\begin{function}
\GLBNS{GetEnergyWindowBins}
{\tt int glbGetEnergyWindowBins(int exp, int rule, int *lowbin, int *highbin)} returns the
energy window in terms of bin numbers [{\tt lowbin}, {\tt highbin}] corresponding to the energy window defined in the \AEDL\ file for the experiment {\tt exp} and rule {\tt rule}.
\end{function}
\begin{function}
\GLBNS{GetNumberOfBins}
{\tt int glbGetNumberOfBins(int exp)} returns the number of bins for the experiment {\tt exp}.
\end{function}
\begin{function}
\GLBNS{GetNumberOfSamplingPoints}
{\tt int glbGetNumberOfSamplingPoints(int exp)} returns the number of sampling points for the experiment {\tt exp}.
\end{function}
\begin{function}
\GLBNS{GetBinSizeListPtr}
{\tt double *glbGetBinSizeListPtr(int exp)} returns a pointer to the array of bin widths
for the experiment {\tt exp}.
\end{function}
\begin{function}
\GLBNS{GetSamplingStepsizeListPtr}
{\tt double *glbGetSamplingStepsizeListPtr(int exp)} returns a pointer to the array of
sampling step sizes for the experiment {\tt exp}.
\end{function}
\begin{function}
\GLBNS{GetBinCentersListPtr}
{\tt double *glbGetBinCentersListPtr(int exp)} returns a pointer to the array of
mean bin energies for the experiment {\tt exp}.
\end{function}
\begin{function}
\GLBNS{GetSamplingPointsListPtr}
{\tt double *glbGetSamplingPointsListPtr(int exp)} returns a pointer to the array of
sampling points for the experiment {\tt exp}.
\end{function}

@@

\index{norm}{Signal!errors}
\index{norm}{Background!errors}
\index{norm}{Background!centers}
Except from the general treatment of systematics, one can read out
and change the signal and background errors for standard pre-defined systematics
during running time:
\begin{function}
\GLBNS{SetSignalErrors}
{\tt int glbSetSignalErrors(int exp, int rule, double norm, double tilt)}
sets the signal errors of experiment {\tt exp} and rule {\tt rule}
to {\tt norm} (normalization error) and {\tt tilt} (tilt/calibration error).
\end{function}
\begin{function}
\GLBNS{GetSignalErrors}
{\tt int glbGetSignalErrors(int exp, int rule, double* norm, double* tilt)}
writes the signal errors of experiment {\tt exp} and rule {\tt rule}
to {\tt norm} (normalization error) and {\tt tilt} (tilt/calibration error).
\end{function}
\begin{function}
\GLBNS{SetBGErrors}
{\tt int glbSetBGErrors(int exp, int rule, double norm, double tilt)}
sets the background errors of experiment {\tt exp} and rule {\tt rule}
to {\tt norm} (normalization error) and {\tt tilt} (tilt/calibration error).
\end{function}
\begin{function}
\GLBNS{GetBGErrors}
{\tt int glbGetBGErrors(int exp, int rule, double* norm, double* tilt)}
writes the background errors of experiment {\tt exp} and rule {\tt rule}
to {\tt norm} (normalization error) and {\tt tilt} (tilt/calibration error).
\end{function}
In addition, the coefficients in the rules can be manipulated by\footnote{Available in GLoBES 3.1.7 and higher.}
\begin{function}
\GLBNS{SetCoefficientInRule} \label{glbSetCoefficientInRule}
{\tt int glbSetCoefficientInRule(int exp, int rule, int pos, int signal, double coeff)}
sets the coefficient of the component {\tt pos} in rule {\tt rule} 
of the experiment {\tt exp} to value {\tt coeff}.
The parameter {\tt signal} refers to signal (\GLBC{GLB\_SIG}) or background
(\GLBC{GLB\_BG}). See also {\tt glbGetCoefficientInRule} on page~\pageref{glbGetCoefficientInRule}.
\end{function}

% ELIMINATED FROM DOC, BECAUSE WE WANT TO AVOID THE BG CENTERS IN THE FUTURE (CONFUSION) [WW]
%
% \begin{function}
% \GLBNS{SetBGCenters}
% {\tt int glbSetBGCenters(int exp, int rule, double norm, double tilt)}
% sets the background centers of experiment {\tt exp} and rule {\tt rule}
% to {\tt norm} (normalization center) and {\tt tilt} (tilt/calibration center).
% \end{function}
% \begin{function}
% \GLBNS{GetBGCenters}
% {\tt int glbGetBGCenters(int exp, int rule, double* norm, double* tilt)}
% writes the background centers of experiment {\tt exp} and rule {\tt rule}
% to {\tt norm} (normalization center) and {\tt tilt} (tilt/calibration center).
% \end{function}
As a more flexible concept, the systematical errors may be given as lists for
both user-defined and built-in systematics. For example, the standard signal and background
pre-defined errors can be accessed as lists with four elements (signal
normalization, signal tilt, background normalization, background tilt) if built-in
systematics is used. The corresponding 
functions are:
\begin{function}
\GLBNS{SetSysErrorsList} 
{\tt int glbSetSysErrorsList(int exp, int rule, int on\_off, const double *sys\_list)}
changes the systematical errors defined in the \AEDL\ file in experiment {\tt exp} and 
rule {\tt rule} to the values in {\tt sys\_list}. This change can be perfomed for
systematics on or systematics off by using {\tt GLB\_ON} or {\tt GLB\_OFF} for {\tt on\_off}. 
\end{function}
\begin{function}
\GLBNS{GetSysErrorsListPtr} 
{\tt double* glbGetSysErrorsListPtr(int exp, int rule, int on\_off)}
returns a pointer to the list of systematical errors as defined in the \AEDL\ file in experiment {\tt exp} and 
rule {\tt rule}. Choose
systematics on or systematics off by using {\tt GLB\_ON} or {\tt GLB\_OFF} for {\tt on\_off}. 
\end{function}
Furthermore, the energy window can be manipulated by\footnote{Available in GLoBES 3.1.7 and higher.}
\begin{function}
\GLBNS{SetEnergyWindow} \label{glbSetEnergyWindow}
{\tt int glbSetEnergyWindow(int experiment, int rule, double low, double high)}
sets the energy window in {\tt experiment} and {\tt rule}, which can be also {\tt GLB\_ALL}. The energy window is limited by the energies {\tt low} and {\tt high}. See also {\tt glbGetEnergyWindow} on page~\pageref{glbGetEnergyWindow}.
\end{function}
As usual, all the set-functions return $-1$ if they were not successful.
%.
For user-defined systematics, see \Sec~\ref{sec:userchi}, and 
for the definitions of these quantities, see \Sec~\ref{sec:rules}.

@@

>>>>

In some cases, it is necessary to obtain information from the loaded \AEDL\
files. This and the next sections are marked as advanced because knowledge of \AEDL\ is
required, \ie,  the reader should be familiar with Part~\ref{part:2} of the manual.
%
The file name of an \AEDL\ file can be retrived with\footnote{The following two functions are available in \GLOBES\ 3.1.7 and higher.}
\begin{function}
\GLBNS{GetFilenameOfExperiment}
{\tt const char *glbGetFilenameOfExperiment(int experiment)} returns the file name of the \AEDL\ file for the experiment number {\tt experiment}. Note that the returned pointer cannot be modified.
\end{function}
and the references to be cited with
\begin{function}
\GLBNS{GetCitationForExperiment} \label{glbGetCitationForExperiment}
{\tt const char *glbGetCitationForExperiment(int experiment)} returns the citation defined in the \AEDL\ file for the experiment number {\tt experiment}. Note that the returned pointer cannot be modified. See also {\tt \$citation} in \AEDL\ on  page~\pageref{citation}.
\end{function}
Very basic information is supplied with
\begin{function}
\GLBNS{GetEminEmax}
{\tt int glbGetEminEmax(int experiment, double *emin, double *emax)} returns the
energy range [{\tt emin}, {\tt emax}] covered by the binning as defined in the \AEDL\ file for the experiment
{\tt experiment}.
\end{function}
\begin{function}
\GLBNS{GetEnergyWindow} \label{glbGetEnergyWindow}
{\tt int glbGetEnergyWindow(int exp, int rule, double *low, double *high)} returns the
energy window [{\tt low}, {\tt high}] defined in the \AEDL\ file for the experiment
{\tt exp} and rule {\tt rule}. See also {\tt glbSetEnergyWindow} on page~\pageref{glbSetEnergyWindow}.
\end{function}
\begin{function}
\GLBNS{GetEnergyWindowBins}
{\tt int glbGetEnergyWindowBins(int exp, int rule, int *lowbin, int *highbin)} returns the
energy window in terms of bin numbers [{\tt lowbin}, {\tt highbin}] corresponding to the energy window defined in the \AEDL\ file for the experiment {\tt exp} and rule {\tt rule}.
\end{function}
\begin{function}
\GLBNS{GetNumberOfBins}
{\tt int glbGetNumberOfBins(int exp)} returns the number of bins for the experiment {\tt exp}.
\end{function}
\begin{function}
\GLBNS{GetNumberOfSamplingPoints}
{\tt int glbGetNumberOfSamplingPoints(int exp)} returns the number of sampling points for the experiment {\tt exp}.
\end{function}
\begin{function}
\GLBNS{GetBinSizeListPtr}
{\tt double *glbGetBinSizeListPtr(int exp)} returns a pointer to the array of bin widths
for the experiment {\tt exp}.
\end{function}
\begin{function}
\GLBNS{GetSamplingStepsizeListPtr}
{\tt double *glbGetSamplingStepsizeListPtr(int exp)} returns a pointer to the array of
sampling step sizes for the experiment {\tt exp}.
\end{function}
\begin{function}
\GLBNS{GetBinCentersListPtr}
{\tt double *glbGetBinCentersListPtr(int exp)} returns a pointer to the array of
mean bin energies for the experiment {\tt exp}.
\end{function}
\begin{function}
\GLBNS{GetSamplingPointsListPtr}
{\tt double *glbGetSamplingPointsListPtr(int exp)} returns a pointer to the array of
sampling points for the experiment {\tt exp}.
\end{function}

@@

\index{norm}{Signal!errors}
\index{norm}{Background!errors}
\index{norm}{Background!centers}
Except from the general treatment of systematics, one can read out
and change the signal and background errors for standard pre-defined systematics
during running time:
\begin{function}
\GLBNS{SetSignalErrors}
{\tt int glbSetSignalErrors(int exp, int rule, double norm, double tilt)}
sets the signal errors of experiment {\tt exp} and rule {\tt rule}
to {\tt norm} (normalization error) and {\tt tilt} (tilt/calibration error).
\end{function}
\begin{function}
\GLBNS{GetSignalErrors}
{\tt int glbGetSignalErrors(int exp, int rule, double* norm, double* tilt)}
writes the signal errors of experiment {\tt exp} and rule {\tt rule}
to {\tt norm} (normalization error) and {\tt tilt} (tilt/calibration error).
\end{function}
\begin{function}
\GLBNS{SetBGErrors}
{\tt int glbSetBGErrors(int exp, int rule, double norm, double tilt)}
sets the background errors of experiment {\tt exp} and rule {\tt rule}
to {\tt norm} (normalization error) and {\tt tilt} (tilt/calibration error).
\end{function}
\begin{function}
\GLBNS{GetBGErrors}
{\tt int glbGetBGErrors(int exp, int rule, double* norm, double* tilt)}
writes the background errors of experiment {\tt exp} and rule {\tt rule}
to {\tt norm} (normalization error) and {\tt tilt} (tilt/calibration error).
\end{function}
In addition, the coefficients in the rules can be manipulated by\footnote{Available in \GLOBES\ 3.1.7 and higher.}
\begin{function}
\GLBNS{SetCoefficientInRule} \label{glbSetCoefficientInRule}
{\tt int glbSetCoefficientInRule(int exp, int rule, int pos, int signal, double coeff)}
sets the coefficient of the component {\tt pos} in rule {\tt rule} 
of the experiment {\tt exp} to value {\tt coeff}.
The parameter {\tt signal} refers to signal (\GLBC{GLB\_SIG}) or background
(\GLBC{GLB\_BG}). See also {\tt glbGetCoefficientInRule} on page~\pageref{glbGetCoefficientInRule}.
\end{function}

% ELIMINATED FROM DOC, BECAUSE WE WANT TO AVOID THE BG CENTERS IN THE FUTURE (CONFUSION) [WW]
%
% \begin{function}
% \GLBNS{SetBGCenters}
% {\tt int glbSetBGCenters(int exp, int rule, double norm, double tilt)}
% sets the background centers of experiment {\tt exp} and rule {\tt rule}
% to {\tt norm} (normalization center) and {\tt tilt} (tilt/calibration center).
% \end{function}
% \begin{function}
% \GLBNS{GetBGCenters}
% {\tt int glbGetBGCenters(int exp, int rule, double* norm, double* tilt)}
% writes the background centers of experiment {\tt exp} and rule {\tt rule}
% to {\tt norm} (normalization center) and {\tt tilt} (tilt/calibration center).
% \end{function}
As a more flexible concept, the systematical errors may be given as lists for
both user-defined and built-in systematics. For example, the standard signal and background
pre-defined errors can be accessed as lists with four elements (signal
normalization, signal tilt, background normalization, background tilt) if built-in
systematics is used. The corresponding 
functions are:
\begin{function}
\GLBNS{SetSysErrorsList} 
{\tt int glbSetSysErrorsList(int exp, int rule, int on\_off, const double *sys\_list)}
changes the systematical errors defined in the \AEDL\ file in experiment {\tt exp} and 
rule {\tt rule} to the values in {\tt sys\_list}. This change can be perfomed for
systematics on or systematics off by using {\tt GLB\_ON} or {\tt GLB\_OFF} for {\tt on\_off}. 
\end{function}
\begin{function}
\GLBNS{GetSysErrorsListPtr} 
{\tt double* glbGetSysErrorsListPtr(int exp, int rule, int on\_off)}
returns a pointer to the list of systematical errors as defined in the \AEDL\ file in experiment {\tt exp} and 
rule {\tt rule}. Choose
systematics on or systematics off by using {\tt GLB\_ON} or {\tt GLB\_OFF} for {\tt on\_off}. 
\end{function}
Furthermore, the energy window can be manipulated by\footnote{Available in \GLOBES\ 3.1.7 and higher.}
\begin{function}
\GLBNS{SetEnergyWindow} \label{glbSetEnergyWindow}
{\tt int glbSetEnergyWindow(int experiment, int rule, double low, double high)}
sets the energy window in {\tt experiment} and {\tt rule}, which can be also {\tt GLB\_ALL}. The energy window is limited by the energies {\tt low} and {\tt high}. See also {\tt glbGetEnergyWindow} on page~\pageref{glbGetEnergyWindow}.
\end{function}
As usual, all the set-functions return $-1$ if they were not successful.
%.
For user-defined systematics, see \Sec~\ref{sec:userchi}, and 
for the definitions of these quantities, see \Sec~\ref{sec:rules}.

@@

\section{Defining oscillation parameter names at running times}

One can either define constants for the non-standard physics parameters, as in our example
\begin{quote}
{\tt
  const int GLB\_SIGMA\_E = 6;  
}
\end{quote}
or assign and read out names dynamically. This feature is available in \GLOBES\ 3.1.7 and higher. The following functions are supported:
\begin{function}
\GLBNS{SetParamName}
{\tt int glbSetParamName(const char *name, int i)} assigns {\tt name} to the oscillation parameter {\tt i} (starting at 0 for {\tt GLB\_THETA\_12}).  
\end{function}
As usual, the return value is $0$ ({\tt GLB\_SUCCESS}) if successful.
Note that the string is copied, which means that the original pointer can be modied or destroyed thereafter.
\begin{function}
\GLBNS{SetParamNames}
{\tt int glbSetParamNames(char **names)} assigns names to all of the oscillation parameters at once. The array of strings {\tt names} must be of length {\tt glbGetNumOfOscParams()}. Individual entries are allowed to be {\tt NULL}.
\end{function}
\begin{function}
\GLBNS{GetParamName}
{\tt char *glbGetParamName(int i)} returns the name of the oscillation parameter {\tt i}.  
\end{function}
\begin{function}
\GLBNS{FindParamByName}
{\tt int glbFindParamByName(const char *name)} returns the number of the oscillation parameter named {\tt name}.
\end{function}
\begin{function}
\GLBNS{SetOscParamByName}
{\tt int glbSetOscParamByName(glb\_params in, double value, const char *name)} sets an oscillation parameter in the structure {\tt in} to {\tt value}. Compared to the similar function {\tt glbSetOscParams}, which parameter is to be accessed is determined by the {\tt name}, not the number.
\end{function}
\begin{function}
\GLBNS{GetOscParamByName}
{\tt double glbGetOscParamByName(glb\_params in, const char *name)} returns an oscillation parameter in the structure {\tt in}. Compared to the similar function {\tt glbGetOscParams}, which parameter is to be accessed is determined by the {\tt name}, not the number.
\end{function}
\begin{function}
\GLBNS{ClearParamNames}
{\tt int glbClearParamNames()} clears all names assigned to oscillation parameters and returns the allocated memory.
\end{function}
